\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{a4wide}
\title{Comparative analysis of my projects}
%\author{not specified}
\date{}
\begin{document}
\maketitle

\section{Generative Models for Missing Data Recovery}
This project will use different techniques to fill in data that is missing in datasets. The techniques are GANs, normalizing flows, diffusion models and BERT.
\begin{enumerate}
\item \emph{The impact} Project enhances the reliability of AI models by enabling them to make predictions even when data is incomplete, thus reducing the need for data preprocessing and improving usability in real-world scenarios.
\item \emph{The consistency} Statistical analysis and experimental validation will confirm the effectiveness of each approach across several datasets and model architectures.
\item \emph{The novelty} Usage of different generative models for data recovery, especially diffusion models and BERT-like architectures.
\item \emph{My contribution} I will experiment with and compare different generative models, and evaluate their impact on AI models for regression and classification tasks.
\item \emph{The project focuses} Demonstrating how generative models can be effectively utilized for missing data recovery and their impact on model performance.
\end{enumerate}

\section{The Impact of Synthetic Data on Text Summarization Quality}
This project explores how using synthetic data improves russian text summarization models.
\begin{enumerate}
\item \emph{The impact} The project explores the potential of synthetic data to enhance summarization quality.
\item \emph{The consistency} Performance will be evaluated using summarization datasets and metrics, ensuring robust and repeatable results.
\item \emph{The novelty} The project uses synthetic data as a means of solving the problem of data scarcity in russian text summarization tasks, comparing its effect across abstractive and extractive methods.
\item \emph{My contribution} I will design and implement synthetic data generation techniques, evaluate their integration into summarization workflows, and measure the resulting impact on model performance.
\item \emph{The project focuses} Demonstrating how synthetic data can address data limitations and improve the effectiveness of summarization models.
\end{enumerate}

\section{Systems of AI equations}
This project explores solving systems of equations derived from interconnected AI models with dependent targets, analyzing the accuracy and stability of these multi-target solutions.
\begin{enumerate}
\item \emph{The impact} This project could improve the efficiency of complex AI applications, especially those with interconnected model dependencies, by developing solutions that optimize and stabilize predictions.
\item \emph{The consistency} Mathematical validation and empirical testing on synthetic and real data will ensure reliable performance.
\item \emph{The novelty} Unlike typical single-target AI models, this project introduces methods for solving interdependent target systems.
\item \emph{My contribution} I will investigate the accuracy and numerical properties of this approach.
\item \emph{The project focuses} Analyzing and improving multi-target AI systems by developing reliable solutions for systems of AI-based equations.
\end{enumerate}

% \section{Resume}
% The project \emph{Title} has the highest priority since, due to; put a brief motivation here. 

\end{document}